Considering scale in multilayer animal social networks

### 2020-06-11 paper/manuscript.Rmd
reorder

### Temporal scale
#### Number of observations
Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks
[@Davis_2018; @Webber_2019]. For example, GPS data is commonly collected at a
fixed rate, e.g. every $x$ minutes or hours, continuously throughout the study
period. Fix rate is a reflection of number of observations an individual would
have been observed and recorded in traditional ethological studies.We
investigated the influence of the number of observations on resulting multilayer
networks. We randomly selected a maximum 485 timesteps for each season to
represent all possible observations. We regenerated multilayer networks and
calculated associations of individuals with 25 additional observations at each
iteration (10 - 485 observations). Subsequent iterations included the previous
set of observations to mimic collection of observational data.

#### Time window length and position
We altered the temporal scale of multilayer networks by varying the length and
position of the time window used to define seasons. The length of the time
window varied from 40-100 days using a fixed start day for summer (starting at 3
August 2017) and winter (starting at 1 January 2018). The position of the time
window was shifted by 1-48 days, using a fixed time window length of 48 days.
These new time windows were iteratively used to partition data into two discrete
seasons (summer and winter) and generate multilayer networks.

>>>>

### Temporal scale
#### Time window length and position
We altered the temporal scale of multilayer networks by varying the length and
position of the time window used to define seasons. The length of the time
window varied from 40-100 days using a fixed start day for summer (starting at 3
August 2017) and winter (starting at 1 January 2018). The position of the time
window was shifted by 1-48 days, using a fixed time window length of 48 days.
These new time windows were iteratively used to partition data into two discrete
seasons (summer and winter) and generate multilayer networks.

#### Number of observations
Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks
[@Davis_2018; @Webber_2019]. For example, GPS data is commonly collected at a
fixed rate, e.g. every $x$ minutes or hours, continuously throughout the study
period. Fix rate is a reflection of number of observations an individual would
have been observed and recorded in traditional ethological studies.We
investigated the influence of the number of observations on resulting multilayer
networks. We randomly selected a maximum 485 timesteps for each season to
represent all possible observations. We regenerated multilayer networks and
calculated associations of individuals with 25 additional observations at each
iteration (10 - 485 observations). Subsequent iterations included the previous
set of observations to mimic collection of observational data.
